%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

\usepackage{fontawesome}
\usepackage{hyperref}

   
% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{001a71}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{000000} %Bold Subsections & Quote
\definecolor{text}{HTML}{C20430} %Highlighted Name
\definecolor{graytext}{HTML}{000000} %Text Information
\definecolor{lighttext}{HTML}{000000} %Address



% \colorlet{awesome}{awesome-red}
% % Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{001a71}

% % Colors for text
% % Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{000000} %Bold Subsections & Quote
% \definecolor{text}{HTML}{940049} %Highlighted Name
% \definecolor{graytext}{HTML}{000000} %Text Information
% \definecolor{lighttext}{HTML}{000000} %Address 




%%%%%%%%%%%%%%%%%%%%%%%%%




% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo{profile.png}
\name{Tevin}{Heath}
%\position{MPA Candidate (2021) {\enskip\cdotp\enskip} Aspiring Local Government Strategist {\enskip\cdotp\enskip} Math \& Stats Graduate}
%\address{Unit 19 - 1 Beaufort Street\\ London, Ontario}
\mobile{(+1) XXX-XXX-XXXX}
\homepage{tevheath.github.io}
\github{TevHeath}
\email{heatht@uoguelph.ca}
% \linkedin{tevin-heath}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{"If you want to go, fast go alone, \\ \textbf{if you want to go far, go together.}"}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {University of Guelph}
  {School of Engineering \\Work Study - Job Title \\ Guelph, Ontario}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Work Study - Job Title}
% How the letter is opened
\letteropening{Dear XXX Professor Name,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Cover Letter Attached}



%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  {Tevin Heath~~~·~~~Cover Letter}
  {\thepage}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
%\doublespacing %removed the doublespacing as it is not a word limit but page limit
\setlength\parindent{24pt}


My name is Tevin Heath, I am a 4th year Bachelor of Science (Hon.) in Mathematics and Statistics at McMaster University graduating in Spring 2020. I am writing this letter applying for admission into Western University’s Masters of Public Administration (MPA - Local Government) full-time program within the Department of Political Science under the Faculty of Social Sciences. 

I would like to start by mentioning that I am extremely grateful to have reached out to alumni and current students of the Western's MPA program for consultation, discussion, and their experiences, despite being currently enrolled as an undergraduate student. From these discussions, it became more clear that the fit of this program would be best suited in my career trajectory. I am grateful for the opportunity to meet full-time students and part-time working professionals, and one of which is currently a student that is from the City of Cambridge. During many of these discussions and my research, I discovered that Western's MPA program has a high emphasis beyond local government, and towards areas such as professionalism, community, and mentorship. This is shown from a wide range of courses, opportunities, and activities such as the alumni conferences where alumnus would meet students, build networks and connect, to the MPA's mentorship program where alumni or working professionals in the part-time program are paired with full-time students towards fostering a mentor-mentee relationship for life-long advice. This high emphasis on community and focus on successful local government job outcomes after graduation is one of the reasons why I am most excited to apply. As the quote above states, “you can't spell community without unity”. Although, there are many reasons why I am excited to be applying another minor compelling reason for me personally is simply because of the location. Currently, my main residence resides in the City of Cambridge. As Western is located in the City of London, it is a manageable commute for me home, if necessary. The location is important because I would like to continue and build my network within the City of Cambridge and design a final research project that focuses on both an immediate and persistent problem in Cambridge while using the courses throughout the MPA program to aid in my administrative, strategic, and public service development. I believe this program would allow me to keep my existing connections and develop a planning study that can be both tangible and meaningful. Finally, I am interested in learning more about specific faculty member's research and advice that relate to my career trajectories. Specifically, Dr. Joseph Lyons and his thoughts on special-purpose bodies and how I can target my career end goal in that area after being accepted and graduating from this program. I place a lot of emphasis on community and being a role model and leader within the City of Cambridge and in the following section, I will go into more detail about why my experiences as a student-leader of mathematics and statistics would make a great fit for the Master of Public Administration program at Western University.

When I began at McMaster University within the Math \& Stats department in the Fall of 2016/2017 after 1 year of Pure Mathematics studies at York University. I became determined to become a student-leader specializing in professionalism, mentorship, and strategy throughout my studies. As a result, I focused on becoming a holistic student-leader that continues to learn and grow in all my coursework, by choosing to develop as a strong assertive communicator and advocate, a compassionate role model who is a team player and consultative for friends, fellow students, and constituents that I may represent or work with,  and to be a great mentor with a mature and poised personality on issues facing undergraduate experiences. These issues faced by undergraduate students are vast and frequent such as emotional \& mental health-related. While ensuring that I give as much effort into my coursework and assignments. I may not be the most academically gifted amongst my graduating class, but I am driven, professional, consultative, poise, and continuously improving and when it came to electing someone to represent the voices of undergraduate student health, policy, or barriers that affect the Department of Mathematics and Statistics, The Faculty of Science, or McMaster University as a whole. I am often selected to be their undergraduate champion. As an undergraduate student, I have been faced with many diverse courses, but to enroll and begin as a graduate student in the MPA program, it would suit me best since I will only be studying what I am most passionate about and would like to learn with the purpose to apply in my career after graduation. As a result, from my experience as a representative, the logical and personal step for me would be to allow my professional, strategic, and administrative development to continue and extend within the Masters of Public Administration with a strong emphasis on local government, as it relates more closely to what I am currently facing and where I see myself in 5+ years after graduation. And for these reasons, I confidently believe that I would be a great asset and a valued full-time student within Western’s MPA (Local Government) program for which I hope to bring a unique perspective in my coursework, discussions, and networking interactions.

In the next section, I will go into further detail about my career goals, specific areas of the program that I am interested in, and how I envision my experience in this program that will help me accomplish them. However, I would like to mention that I am a non-traditional student, with a breadth of leadership experience. As mentioned to me from a part-time student within the program, they mentioned that it is okay to be a non-traditional student. As such, the study of Mathematics and Statistics although it does not teach the fundamentals of policy analysis, evaluations, or public policy instead it trains us on how to remain objective, critical, and logical in our thinking, coupled with evidence-based statistical analysis, techniques, and tools. I believe this gives me the freedom to grow a skill set that is distinct within the Master of Public Administration program. Throughout my undergraduate studies, I ensured to develop a diverse range of knowledge from different academic disciplines. Also, utilizing my professional and leadership experiences of being an interdependent and collaborative learner. It has allowed me to balance both the challenge technical skills from my coursework with, the leadership and communication skills from my professional, leadership and volunteer activities.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
