%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ \scshape Leadership Activities \& Development}

\cvsubsection{\scshape McMaster University}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Research Committee: Undergraduate Board-Reviewer} % Affiliation/role
    {Hamilton Integrated Research Ethics (HIREB), } % Organization/group
    {Hamilton Health Sciences} % Location
    {Sept. 2011 - PRESENT} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] {Hamilton Integrated Research Ethics Board (HIREB), Student Research Committee (SRC) is a subcommittee of the HiREB.  Their mandate is to review minimal risk research conducted by Faculty of Health Science students at the undergraduate and master’s levels.}
        \begin{itemize} 
        \item {Recruited to be one of the 8 Undergraduate/Graduate students to serve on the Hamilton Integrated Research Ethics (HiREB) – Student Research Committee (2-year term)}
        \item {Accountable for reviewing protocols to ensure adequate consideration and safeguards that meet acceptable ethical, clinical and scientific standards.}
        \end{itemize}
      \end{cvitems}
    }


%---------------------------------------------------------
%   \cventry
%     {Anthropology, Religious, Geography Student Research Ethics Committee: Undergraduate Board-Reviewer} % Affiliation/role
%     {McMaster University Research Ethics Board (MREB)} % Organization/group
%     {McMaster University} % Location
%     {Aug. 2017 - PRESENT} % Date(s)
%      {\renewcommand{\labelitemii}{\bullet}
%       \begin{cvitems}% Description(s) of tasks/responsibilities
%         \item[] {Find the description for this Board}
%         \begin{itemize} 
%         \item {Serving 3-year term Anthropology, Religious Studies, Geography Student Research Ethics Committee (ARGSEC}
%         \end{itemize}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {Emerging Health Leader Graduate} % Affiliation/role
    {\href{https://www.linkedin.com/feed/update/urn:li:activity:6443522898333442048/}{McMaster University's Health Leadership Academy}} % Organization/group
    {McMaster University} % Location
    {Aug. 2018 - Sept 2018} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] {The Emerging Health Leaders (EHL) Program was a two-week intensive, residential, leadership program for students and young professionals from across Canada and beyond. With a focus on personal leadership development, collaborative team engagement, and change management capabilities, the Emerging Leaders Program will push you to become a better leader.}
        \begin{itemize} 
            \item {As a graduate this two-week extensive leadership program it has aided in my  on-going ability to lead, mentor, strategize, and collaborate}
            \item{The Emerging Health Leader program opened doors and my interests towards specialized areas in Strategic Health Leadership and Healthcare-Related Decision Making \& Governance}
            \item{This professional-leadership development program provided training within the areas of Strategic Health Leadership, Health Strategy, Health Leadership, and Health-Related Decision Making}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Executive Undergraduate Member} % Affiliation/role
    {Ad-Hoc Selection Committee for New Chair of the Mathematics and Statistics Department} % Organization/group
    {Faculty of Science} % Location
    {Jan. 2018 - May. 2018} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        \item[] {Ad-Hoc committee formed by the Dean of Science at McMaster University towards a process in selected a new Chair for the Department of Mathematics and Statistics, this committee consisted of the following: \\Dean of the Faculty of Science, 4 Faculty members from the Department of Mathematics \& Statistics, 1 Faculty member outside the Department of Mathematics \& Statistics, 1 Staff member from the Department of Mathematics \& Statistics, 1 Graduate Student from the Department of Mathematics \& Statisitics, 1 Undergraduate Student from the Department of Mathematics \& Statistics. }
        \begin{itemize} 
        \item {Selected by the Department of Mathematics and Statistics to be a voting undergraduate member during the process to select a new Chair of the Mathematics and Statistics Department at McMaster University.}
        \item {Assisted in the design of the survey to be disseminate to the undergraduate student studying Mathematics and Statistics.}
        \item {Aided in the review and input of the designed question towards the applicants and interviewee's.}
        \item {Actively engaged and provided input on behalf of the mathematics and statistics undergraduate students.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\vspace{0.25cm}
% \cvsubsection{\scshape Healthcare Affiliations}

% \begin{cventries}
% %---------------------------------------------------------
% \cventry
%     {Student Member} % Affiliation/role
%     {Ontario Public Health Association} % Organization/group
%     {Toronto, Ontario} % Location
%     {Sept. 2019 - PRESENT} % Date(s)
%      {\renewcommand{\labelitemii}{\bullet}
%       \begin{cvitems}% Description(s) of tasks/responsibilities
%         \item[] {University Planning committee is the most senior planning committee responsible for academic planning, management resources and serves as an advisory role to the Senior Administration of McMaster University.}
%         \begin{itemize} 
%         \item {Elected term 2-year, effective July 1, 2018}
%         \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
%         \end{itemize}
%       \end{cvitems}
%     }
% %---------------------------------------------------------
%   \cventry
%     {Student Member} % Affiliation/role
%     {Canadian Public Health Association} % Organization/group
%     {Ottawa, Ontario} % Location
%     {Dec. 2018 - PRESENT} % Date(s)
%      {\renewcommand{\labelitemii}{\bullet}
%       \begin{cvitems}% Description(s) of tasks/responsibilities
%         \item[] {University Planning committee is the most senior planning committee responsible for academic planning, management resources and serves as an advisory role to the Senior Administration of McMaster University.}
%         \begin{itemize} 
%         \item {Elected term 2-year, effective July 1, 2018}
%         \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
%         \end{itemize}
%       \end{cvitems}
%     }
% \end{cventries}