%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ \scshape Volunteer Activities}

\cvsubsection{\scshape McMaster University}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Mentor} % Affiliation/role
    {MacPeer Mentorship} % Organization/group
    {Student Wellness Centre} % Location
    {Sept. 2018 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in penetration testing areas, especially targeted on web application and software.}
        \item {Participated on a lot of hacking competition and won a good award.}
        \item {Held several hacking competitions non-profit, just for fun.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mentorship Lead} % Affiliation/role
    {McMaster English Development Course (M.E.L.D)} % Organization/group
    {McMaster University} % Location
    {Sept. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in hardware hacking areas from penetration testing on several devices including wireless router, smartphone, CCTV and set-top box.}
        \item {Trained wannabe hacker about hacking technique from basic to advanced and ethics for white hackers by hosting annual Hacking Camp.}
      \end{cvitems}
    }
%---------------------------------------------------------

  \cventry
    {Chair \& Board Member} % Job title
    {Peer Conduct Board}
    {McMaster University} % Location
    {Aug. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
      \end{cvitems}
    }
\end{cventries}
%---------------------------------------------------------
\cvsubsection{\scshape York University}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Class Representative} % Affiliation/role
    {Faculty of Science (Bethune College)} % Organization/group
    {York University, Toronto} % Location
    {Oct. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Reformed the society focusing on software engineering and building network on and off campus.}
        \item {Proposed various marketing and network activities to raise awareness.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {First Year Undergraduate Member} % Affiliation/role
    {Science Student Caucus} % Organization/group
    {York University, Toronto} % Location
    {Oct. 2015 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
        \item {Participated on several hacking competition and won a good award.}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }

%---------------------------------------------------------
%   \cventry
%     {First Year Undergraduate Member} % Affiliation/role
%     {Faculty of Science Council} % Organization/group
%     {York University, Toronto} % Location
%     {Oct. 2015 - Apr. 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
%         \item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
%       \end{cvitems}
%     }
%---------------------------------------------------------
%   \cventry
%     {Senator} % Affiliation/role
%     {Faculty of Science} % Organization/group
%     {York University, Toronto} % Location
%     {Jan. 2016 - Apr. 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item Successfully won election but Declined due to Transfer to McMaster University starting Fall 2016)
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
