%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{\scshape Employment}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {City of Calgary, Supply Management \& Procurement} % Affiliation/role
    {Supply \& Project Management  \textsc{Summer Intern} (4-month)} % Organization/group
    {Calgary, Alberta } % Location
    {May. 2024 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item As a summer student within my first month at the City of Calgary took the responsibility to software engineer the City of Calgary's Supply Chains first an \textbf{Automation Program} \textit{(refer to Internship Project Section)} using both Python and R scripts. This automation program allowed for data collection and  data pipe-lining without data loss to be completed at a scheduled automated time.  
        \item Assisted in the development, documentation, and performance of master data quality checks across the data assets and maintained data quality assurance throughout the data repositories to ensure the quality of data delivered to internal interested parties and the public from our various products within the City of Calgary Supply Chain Management.
        \item Designed data pipelines and the software architecture that utilized information from a wide range of data source systems into a system pipeline that allows Business Analysts to analyze and generate reports using PowerBI.
        % \item Define the respective data model and underlying data structures. Develop and manage a data model which provides the details of City information, how it is to be stored.
        \item Liaison between interested parties (i.e., projects specialist, system architects, data analyst) on develop a good understanding of the business context, provide expert technical judgement and analysis for the architecture design, development, and implementation of diverse types of data solutions including integration, migration, reporting, data warehousing and application data layer.
        \item Taught, performed, led live tutorials for non-technical specialist and leadership on data management, data sourcing, and collection methods of modern methods of data transformation and distribution using Python and R and reporting using Microsoft Excel \& PowerBI.
        \item Assisted the team with designing descriptive, prescriptive and predictive models by utilizing machine learning techniques through Python packages \& modules such as TensorFlow, Selenium, and Pandas.
        % \item Worked closely with other external Project Specialists, System Architects,  Business Intelligence Analyst and Data Analysts on architecture solutions that integrate, consolidate, cleanse and structure data for use in analytics and dashboard applications.
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Freelancer} % Affiliation/role
%     {1st Year Linear Algebra Tutor} % Organization/group
%     {On-call} % Location
%     {January 2024  - April 2024} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item Design Linear Algebra curriculum for .
%         \item Assisted 2-4 student on problems sets aimed at mastery, by providing questions and concepts to review.
%         \item Taught and mentored practice problems, by allowing students to learn indepedently while being available for assistance.
%       \end{cvitems}
%     }


% %---------------------------------------------------------
%   \cventry
%     {Freelancer} % Affiliation/role
%     {Website \& Application Developer} % Organization/group
%     {Remote} % Location
%     {August 2023 - PRESENT} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item Highlight git/github.
%         \item Highlight CSS and Javascript.
%         \item Mention the website.
%         \item Highlight the amount of commits and daily pushes.
%       \end{cvitems}
%     }



%---------------------------------------------------------
  \cventry
    {University of Guelph, Laboratory Services} % Affiliation/role
    {Financial \& Accounting Analyst,  \textsc{Work-Study Intern} (4-month)} % Organization/group
    {Guelph, Ontario } % Location
    {Sept. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Selected and hired as part of the\textbf{ University of Guelph Work-Study Program} that allows for students to apply their academic program (i.e., Computer Engineering) with part-time works that relates to their career interest and goals.
        \item Designing a financial software with the Finance Manager aimed at automating the manual and labour intensive processes, using Python another other additional scripting languages.
        \item Assisting in gathering and analyzing data related to outstanding receivables, and provide assistance as required to the Accounts Receivable Coordinator.
        \item Helping to collect outstanding balances on delinquent client accounts.
        \item Import invoicing batches on a daily basis and post invoice batches to ACCPAC.
        \item Enter payment for all external clients, via cash, cheques, credit/ debit cards and electronic bank transfer; electronically transfer VISA/MasterCard payments via the credit card terminal to the bank.
        \item Provide coverage for purchasing team to create orders, and complete paper filling.
        \item Assist in the preparation of financial reports.
        \item Support special projects and initiatives.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Cambridge Memorial Hospital} % Affiliation/role
    {Data \& Decision Support \textsc{Intern} (4-month)} % Organization/group
    {Cambridge, Ontario } % Location
    {Jun. 2022 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Developed dashboards using PowerBI and Python, based on program needs, to support ongoing performance and quality measurement, planning, and reporting.
        \item Promoted information-driven decision making at all organizational levels.
        \item Applied high quality data (i.e. Health Records, Meditech, Case Costing, etc.) and information to support appropriate resource allocation and informed decision making at all levels.
        \item Worked with Managers to identify and develop clinical performance and outcome indicators for their programs.
        \item Assisted in programs development through interpretation, analysis, and presentation of clinical performance data and the development of action plans to address areas that require improvement.
        \item Developed and support the web UI/UX for the customers who interact with Decision Support Data.
        \item Provided consultancy services of healthcare funding methodologies (HBAM and QBP).
        \item Demonstrated experience in database design, data modelling and administration of SQL databases.
        \item Designed professional presentations and reports to an engaged a knowledgeable audience.
      \end{cvitems}
    }




%---------------------------------------------------------
  \cventry
    {Homewood Health Inc.} % Affiliation/role
    {Business \& Data Analyst \textsc{Intern} (3-month)} % Organization/group
    {Guelph, Ontario } % Location
    {Apr. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Utilized software's and databases (e.g., SQL, Python, and Tableau) to design applications and dashboard to provide reports and timely information for senior executive for Homewood Health Inc. including the President and Vice-Presidents.
        \item Designed and worked through star-flake schema's to determine necessary databases and data structures for data retrieval and data reporting dashboard and modules.
        \item Participated in process and data source improvement initiatives by designing, writing and implementing process documentation based on collecting business and process requirements.
        \item Managed multiple projects and provided deliverables to a wide range of audiences while assisting senior management on understanding of how to interpret stakeholder business needs and translate them into application and operational requirements.
        \item Led design projects for the creation of a cohesive set of reports to assist operational leaders manage their business areas according to external Service Level Agreements (SLAs) and Internal Key Performance Indicators (KPIs).
        \item Supported stakeholders with analysis and ad-hoc information requests including performance metrics through compilation and interpretation of data pulled from various resources according to established timelines.
        \item Published and created applications and reporting dashboard designed to forecast and track business performance and trends by analyzing collected data.
        \item Implemented effective Business Intelligence (BI) tools using business intelligence data and information to produce actionable analysis.
        \item Critically evaluated information across multiple sources, reconcile conflicts, decompose high-level data into details and abstract up from low-level data to a general understanding of the information.
      \end{cvitems}
    }


%---------------------------------------------------------

  \cventry
    {KPMG Canada} % Affiliation/role
    {Senior Consultant \textsc{Intern} (8-month)} % Organization/group
    {Waterloo, Ontario } % Location
    {Oct. 2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Provided consultancy services for public and municipal sector clients by analyzing, evaluating, and developing business solutions, KPI’s and strategic processes (financial, operational, risk, and system processes).
        \item Identify organizational and/or project local government opportunities for improvement and streamlining of municipal government processes.
        \item Developed and performed business analyses of functional requirements to identify information, procedures, decision flows, and document statements of requirements for considered alternatives.
        \item Developing and/or implementing an organizational improvement plan, business plan, policies, and standards.
        \item Making recommendations and providing advice for improvements and assisting in developing solutions, scenarios and implementing recommendations.
        \item Lead junior staff consultants in assisting the project team in all management activities including financial planning and contracting aspects.
        \item Designer in developing adequacy of current performance measurement frameworks and performance measures in the municipal government, there the direction and design of process maps towards understanding local government organizational model and system processes.
        \item Assist in stakeholder consultation and conversation in the development and implementation of public sector strategy and business improvement processes and programs.
        \item Supported all team members and was responsible for the management of stakeholder interviews, process mapping exercises, report writing, team and stakeholder coordination, technical programming of data analytics \& visualization, project engagements and statistical assistance.
        \item Supporting the planning execution, and completion of client management and consultancy engagement reviews Canadian local government clients.
        \item Acted as the primary point of contact with senior members of client management and scheduling and ensuring the ongoing maintenance of project deliverables and professional relationships.
        \item Wrote and edited technical and documentation reports for stakeholders, clients, and customers on a client facing level.
        \item Oversaw all the submitted written report and technical documentation from junior consultant and mentored their progress prior to client meetings.
      \end{cvitems}
    }




%---------------------------------------------------------




%---------------------------------------------------------
  \cventry
    {City of London} % Affiliation/role
    {Municipal Supervisor \textsc{Intern} (5-month) } % Organization/group
    {London, Ontario } % Location
    {Jun. 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Hired part of the London, Ontario's Local Government Management training program, designed to trained scholarly University Graduates on managerial skills within the Public Sector as a potential career option.
        \item Supervision internship position targeted to develop municipal customer service, planning, coordination, supervision, and management for the City of London.
        \item Provided maintenance leadership and oversaw duties of staff for the South London Arena’s and Community Centre.
        \item Showcased excellent customer service and professionalism to members of the public entering London’s community centers.
        \item Displayed administrative and managerial functions by providing leadership to building staff will conducting facility maintenance, cleaning, disinfecting tasks and rental set up.
      \end{cvitems}
    }

%---------------------------------------------------------





% %---------------------------------------------------------
%   \cventry
%     {Sport Chek} % Affiliation/role
%     {Senior Sales Associate} % Organization/group
%     {Kitchener, Ontario } % Location
%     {Dec. 2011 - Dec. 2022} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item Promoted to the position of Senior Sales Associate, December 2016.
%         \item Committed 10 years to the Sport Chek community and able to remain part of the Sport Chek philosophy during undergraduate studies and graduate studies.
%         \item Hired Sales Advisor since December 2011, developed professional communication skills with public, customers, managers, stakeholder, professional athletes (NBA \& NHL) that visited Sport Chek.
%         \item Remain positive, respectful, and inspirational to all demographics and diverse groups with care and warmth on sensitive topics such as weight, appearance, athletic abilities, or capabilities.
%         \item Always remained patient and poise with customer to ensure their product needs are handled with care. Consistently trained over 50+ new associates about customer relations, product knowledge, customer service ethics, and respectful communication over 10-year work experience.
%       \end{cvitems}
%     }

% %---------------------------------------------------------



%---------------------------------------------------------
\end{cventries}
