%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ \scshape Professional Activities}

\begin{cventries}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
  \cventry
    {\href{https://secretariat.mcmaster.ca/senate/}{McMaster University's Senate}} % Job title
    {Senator} % Organization
    {Hamilton, Ontario} % Location
    {Jul. 2018 - Jun. 2020} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        % \item[] {McMaster University's Senate is the highest academic governing body at McMaster University for which we make decisions on all academic-related issues such as;  - Academic Integrity - Appointments - By-Laws - Honorary Degrees - Student Affairs - University Ceremonials \& Insignia - Student Appeals - Tenure and Promotions:}
        % \begin{itemize} 
         \item {Elected on a term 2-year, effective July 1, 2018, ending on June 30, 2020.}
        \item{Successfully campaigned and advocated at over 30+ class talks, lectures and events during a strict 2-week campaign period.}
        \item {Elected to represent the vision of the Faculty of Science through the eyes of undergraduate science population on McMaster University's Senate on all academic issues, concerns, policy, and program implementations affecting Faculty of Science students at McMaster University.}
        \item{Elected by the undergraduate student's population from the Faculty of Science consisting 6000+ science students to be their representative on The Senate.}
        \item{Appointed by the Executive Council to the following Subcommittee's:}
        \begin{itemize}
            \item {Student Appeal Tribunal Panel}
            \item {Board-Senate Hearing Panel for Discrimination, Harassment, and Sexual Violence Panel}
         \end{itemize}
        \item {Debated confidently with McMaster University's \textbf{Deans}, \textbf{Chairs}, and \textbf{Faculty} during McMaster University's open \& closed Senate meeting on topics such as undergraduate student experience, culture, empowerment, policy, and mental health.}
        % \end{itemize}
      \end{cvitems}
    }
%-------------------------------------------------------------------------------

  \cventry
    {\href{https://financial-affairs.mcmaster.ca/services/budgeting/budget-committee/2018-19-membership-listing/}{McMaster University's Budget Committee}} % Job title
    {Undergraduate Student Representative} % Organization
    {Hamilton, Ontario} % Location
    {Jul. 2018 - Jun. 2020} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        % \item[] {The Budget Committee is one of the many executive committee's at McMaster University and an influential sub-committee the University Planning Committee, that is responsible and accountable for reviewing the budget framework, and for preparing the operating budget for McMaster University to be by  recommendation to the Board of Governors.}
        \vspace{0.1cm}
            % \begin{itemize} 
                \item {Served a 2-year an appointed term on the McMaster University's Budget Committee, effective July 1, 2018.}
                \item {Appointed to be the only undergraduate representative to review McMaster University \$1.075b+ Budget by the Executive Administration of McMaster University including the \textbf{President, Vice-Presidents, Provost,} and \textbf{Chief Financial Officer}.}
                \item {Appointed as a voting undergraduate member for all 26,000+ undergraduate student as an undergraduate representative on the long-and short-term planning budgeting decisions affecting McMaster University as a leading Research-Intensive University.}
                \item {Demonstrated highly informative strategic decision-making on concerns about funding, budgeting, global-relations that influence the undergraduate population and invested stakeholders both on a short-term and long-term scale.}
                \item {Reported directly to \textbf{Chair of the Budget Committee} and assists McMaster University's Executive Administration such as the \newline President, CFO, and VP's on sound financial insights, implications, and solutions that affect the undergraduate student population.}
            % \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------

  \cventry
  {\href{ https://secretariat.mcmaster.ca/app/uploads/2019/03/Membership-List-1.pdf}{Committee to Recommend a New President for McMaster University}} % Job title
     {Undergraduate Student Representative} % Organization
    {Hamilton Ontario} % Location
    {Jan. 2019 - Dec. 2019} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        % \item[] {Senior Executive committee was formed to oversees, designs, and implement the recommendation for the next President for McMaster University starting July 1, 2020. This committees includes five members appointed by McMaster University's Board of Governors and five members appointed by the McMaster University's Senate.}
        % \begin{itemize} 
        \item {Selected by McMaster University's Senate to be the Undergraduate Executive Committee Member representing all Full-time/Part-time \& Medical Students on the \textbf{Executive Search Committee to Recommend a New President.}}
        \item{Collaborated as a team and committee member in the design recruitment cycle, university-wide consultation, and formulation interview questions during the long-list selection, short-list selection, and subsequent interviews, with the guidance of our selected Search Consultancy Firm.}
        \item{Trained extensively on Equity, Diversity, and Inclusion provided by McMaster University's \textbf{Associate Vice-President, Equity and Inclusion}, to ensure a strong Management of Unconscious Bias and Inclusive Excellence prior and during to the Presidential Selection Process.}
        \item{Involved thoroughly with dialogue and consultations with McMaster University's Public Relations Team, Communication Office, International Recruitment Office, University's Advancement, Board of Governors, and McMaster Student \& Faculty Unions, invested stakeholder groups and selected Search Consultancy Firm - Boyden on recruitment, reach, and McMaster University Culture.}
        \item{Maintained healthy dialogue with \textbf{Executive Search Consultancy Firm, Boyden } selected by interview to Presidential Search Process by providing constant communication and supportive feedback.}
        \item{Exercised mature \& supportive professionalism with all committee members, stakeholders and interviewee's throughout all the discussion, engagements, and interviews during the Presidential Search Committee tenure.}
        \item {Adhered masterfully and ethical to the confidential \& privacy agreement during the Executive Presidential Search for the safety of the applicants, interviewee's, and overall integrity of McMaster University as a leading Research-Intensive University.}
        % \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
\vspace{0.25cm}
  \cventry
   {\href{https://secretariat.mcmaster.ca/app/uploads/2019/01/2018-2019-UPC-membership-1.pdf}{McMaster University's Planning Committee}} % Job title
    {Undergraduate Student Representative} % Organization
    {Hamilton, Ontario} % Location
    {Jul. 2018 - Jun. 2020} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        % \item[] {University Planning committee is the most senior planning committee responsible for academic planning, management resources and serves as an advisory role to the Senior Administration of McMaster University.}
        \vspace{0.1cm}
            % \begin{itemize} 
                \item {Served a 2-year elected term on the University Planning Committee, effective July 1, 2018.}
                \item {Elected by the undergraduate students (Full-time/Part-time \& Medical Students) to be their executive representative and voice on \newline strategic plans and developments at McMaster University.}
                \item{Reported directly to the Chair of the Committee - McMaster University's\textbf{ Provost \& Vice-President (Academic)} and the \textbf{Associate Vice-President, Finance and Planning (Academic)} on inquiries and concerns relating to planning issues may affect the undergraduate student populations academically, administratively, and strategically.}
                \item{Exercised sound judgment and consultation of student experiences and stakeholder dialogue on long-term issues and planning concerns that impact McMaster University strategically.}
                \item {Maintained a poised, consultative, and assertive level of engagement on McMaster University's Planning Committee about student experiences and challenges on behalf of all the 26,000+ undergraduates students.}
            % \end{itemize}
      \end{cvitems}
    }
% https:/
%---------------------------------------------------------


  \cventry
    {McMaster University's Student Appeals Tribunal} % Organization
    {Undergraduate Tribunal Member} % Job title
    {Hamilton, Ontario} % Location
    {Jul. 2018 - Jun. 2020} % Date(s)
     {\renewcommand{\labelitemii}{\bullet}
      \begin{cvitems}% Description(s) of tasks/responsibilities
        % \item[] {The Senate-Board for Student Appeals adjudicates all student appeals. Membership includes the appointment of four undergraduate students by McMaster University's Senate.}
        %     \begin{itemize} 
                \item {Given assignments and cases to review student appeal cases using the Academic Integrity Policy and Student Appeal Tribunal procedural guidelines at McMaster University.}
                \item{Worked closely with the \textbf{McMaster University's Lawyer on Student Appeals Cases}, on ensuring the outcome is fair based on the balance of probabilities per the Academic Integrity Policy. }
                \item {Aided the Chair of each tribunal hearing with questions and tribunal procedures towards investigating the principles of procedural fairness, adjudicating penalties at the Tribunal \& by listening to concerns at hearings.}
                \item {Demonstrated and displayed ethical and fair judgment on the evidence provided prior, during and after the hearing. To assess the penalties and purpose of the student appeals.}
            % \end{itemize}
      \end{cvitems}
    }
    
%---------------------------------------------------------
%  \cventry
%     {Tribunal Member} % Job title
%     {McMaster University's Board-Senate Hearing Panel for Discrimination, Harassment and Sexual Violence} % Organization
%     {McMaster University} % Location
%     {Jul. 2018 - PRESENT} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Researched means of retrieving a corresponding video based on image contents using image similarity algorithm.}
%         \item {Implemented prototype that users can obtain torrent magnet links of corresponding video relevant to an image on web site.}
%       \end{cvitems}
%     }
%---------------------------------------------------------

\end{cventries}