%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ \scshape Volunteer Activities}

\cvsubsection{\scshape McMaster University}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Campus Communicators Toastmasters Club} % Affiliation/role
    {Club Member} % Organization/group
    {Western University} % Location
    {Jul. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Newly joined member of Campus Communicators Toast Masters. Club Communicators appeals to a wide audience: faculty and staff of the university, graduate and undergraduate students, and members of the London community who like the connection with the university.}
        \item {Delivered Table topics and Ice-breakers speeches in front of club members and guest to ensure positive and support atmosphere.} 
        \item{Toastmasters is an international, non-profit organization that provides individuals a friendly, fun, \& encouraging environment to improve their communication \& leadership skills. We learn by active participation - by running meetings, giving speeches, evaluating speakers \& by giving impromptu talks followed by friendly, positive oral \& written feedback provided by other members.}
        \end{cvitems}
      }
    

%---------------------------------------------------------
  \cventry
    {MacPeer Mentorship} % Affiliation/role
    {Lead Mentor} % Organization/group
    {McMaster University} % Location
    {Sept. 2018 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Displays peer mentorship towards at-risk students at McMaster University struggling with in social anxiety through peer-to-peer relationship building and engagement, and communication skills.}
        \item{Designing, plan, and execute activities to create a collaborative environment such that mentees feel comfortable to develop self-confidence with interacting with others.}
        \item {Maintains a healthy relationship and peer support with mentee during exams and mental health crises.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sonnadara Performance Science Lab, Department of Surgery} % Organization/group
    {Junior Research Assistant (Volunteer)} % Affiliation/role
    {McMaster University} % Location
    {April. 2018 - June 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Under the Supervision of Dr. Kiret Dhindsa as Research Supervisor, aided in conducting research and machine learning analysis and methods on core projects of Predicting Stimulus, Task, and Response accuracy from intracranial EEG in Epileptic Patients.}
        \item {Learned about Advanced Physics, Mathematical, and Machine Learning/Programming concepts such as signal processing tools for \newline Multichannel time series (iEEG) in Python, by using and including including normalization, spatial filters, digital filters, spectral analysis, auto- regression, and artifact correction.}
        \item {Learned to apply and build and train machine learning models in Keras and Tensorflow and to evaluate these predictive models in a statistically valid way.}
      \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {McMaster University's Peer Conduct Board} % Job title
    {Chair \& Board Member}
    {McMaster University} % Location
    {Aug. 2016 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Appointed to the be the Chair of the Peer Conduct Board, September 2017}
        \item {Chaired cases brought before the board, which includes: Leading \& following the structure of the hearing, listening to testimony of student and residence manager}
        \item {Managed, reviewed and clarified with the other committee members where responsibilities were not upheld and assigning outcomes to ensure restorative and natural justice.}
        \item {Consulted and trained board members and corresponding committees on the judicial process under the Student Code of Conduct, Residence Code of Conduct, and Athletic Code of Conduct to ensure restorative justice.}
      \end{cvitems}
    }
 


    
%---------------------------------------------------------

 \cventry
 {Student Success Centre, McMaster University} % Organization/group
    {Peer Language Facilitator \& Mentor} % Affiliation/role
    {McMaster University} % Location
    {Sept. 2016 - Apr. 2017}
     % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Delivered one-on-one support, guidance, and mentorship one-hour a week for participants that have English-as-an-Additional Language (EAL).}
        \item {Assisted participants with language in command through strengthening discussions by aiding patiently with pronunciations, idioms, slang, grammar, vocabulary, and flow.}
        \item {Constructed and led language programs, activity, and culturally sensitive games designed to empowering self-confidence in speech and verbal communication, and  adjustment for participants to the Canadian culture.}
      \end{cvitems}
    }

%---------------------------------------------------------
% \cvsubsection{\scshape York University}

% \begin{cventries}

% %---------------------------------------------------------
%   \cventry
%     {Faculty of Science (Bethune College)}  % Organization/group
%     {Class Representative} % Affiliation/role
%     {York University, Toronto} % Location
%     {Oct. 2015 - Apr. 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item {Reformed the society focusing on software engineering and building network on and off campus.}
%         \item {Proposed various marketing and network activities to raise awareness.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {Science Student Caucus} % Organization/group
%     {First Year Undergraduate Member} % Affiliation/role
%     {York University, Toronto} % Location
%     {Oct. 2015 - Apr. 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item {Gained expertise in hacking \& security areas, especially about internal of operating system based on UNIX and several exploit techniques.}
%         \item {Participated on several hacking competition and won a good award.}
%         \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
%         \item {Conducted penetration testing commissioned by national agency and corporation.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {First Year Undergraduate Member} % Affiliation/role
%     {Faculty of Science Council} % Organization/group
%     {York University, Toronto} % Location
%     {Oct. 2015 - Apr. 2016} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of experience/contributions/knowledge
%         \item {Gained knowledge about several business field like Management, Strategy, Financial and marketing from group study.}
%         \item {Gained expertise in business strategy areas and inisght for various industry from weekly industry analysis session.}
%       \end{cvitems}
%     }
% %---------------------------------------------------------
  \cventry
    {Senator} % Affiliation/role
    {Faculty of Science} % Organization/group
    {York University, Toronto} % Location
    {Jan. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Successfully won election but Declined due to Transfer to McMaster University starting Fall 2016
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
